---
title: 'Predict credit card approval'
author: "Yameng Guo"
date: "10/25/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

# Load own subset
```{r, warning=FALSE}
library(dplyr)
library(psych)
data1 <- read.csv("Group4_data3.csv", header = T)
dim(data1)
str(data1)
describe(data1)
```

# Categorical features into factor data type
```{r, warning=FALSE}
data2 <- data1[,-c(1,19)]
convert <- c(2:5, 7:9,16)
data2[,convert] <- lapply(data2[,convert], as.factor)
data2$TARGET <- as.factor(data2$TARGET)
str(data2)
```


# Feature selection
```{r,echo = FALSE,, warning=FALSE}
library(caret)
library(randomForest)
set.seed(100)
rPartMod <- train(TARGET~., data=data2, method="rpart")
rpartImp <- varImp(rPartMod)
print(rpartImp)
plot(rpartImp, top = 20, main='Variable Importance')
```

# Select predictors
```{r, warning=FALSE}
data3 <- data2 %>% select(AMT_INCOME_TOTAL,DAYS_BIRTH,FLAG_OWN_REALTY,NAME_EDUCATION_TYPE,
                          BEGIN_MONTHS,CNT_CHILDREN,TARGET)
```

# Create train and test datas
```{r, warning=FALSE}
set.seed(10152021)
splitSample <- sample(1:2, size=nrow(data3), prob=c(0.45,0.55), replace = TRUE)
train_45 <- data3[splitSample==1,]
test_55 <- data3[splitSample==2,]

set.seed(10152021)
splitSample <- sample(1:2, size=nrow(data3), prob=c(0.65,0.35), replace = TRUE)
train_65 <- data3[splitSample==1,]
test_35 <- data3[splitSample==2,]

set.seed(10152021)
splitSample <- sample(1:2, size=nrow(data3), prob=c(0.85,0.15), replace = TRUE)
train_85 <- data3[splitSample==1,]
test_15 <- data3[splitSample==2,]
```

# ##############################################################################
# ############################### KNN Model ####################################
# Extract x and y
```{r, warning=FALSE}
library(caret)
library(Matrix)
#library(e1071)
library(class)

train_45x <- train_45 %>% select(-TARGET)
train_45y <- train_45 %>% select(TARGET)
test_55x <- test_55 %>% select(-TARGET)
test_55y <- test_55 %>% select(TARGET)

train_65x <- train_65 %>% select(-TARGET)
train_65y <- train_65 %>% select(TARGET)
test_35x <- test_35 %>% select(-TARGET)
test_35y <- test_35 %>% select(TARGET)

train_85x <- train_85 %>% select(-TARGET)
train_85y <- train_85 %>% select(TARGET)
test_15x <- test_15 %>% select(-TARGET)
test_15y <- test_15 %>% select(TARGET)

```

# Normalization the predictors of training and testing subsamples
```{r, warning=FALSE}
normalize <- function(x){return((x-min(x))/(max(x)-min(x)))}
train_45x[,c(1,2,5)] <- lapply(train_45x[,c(1,2,5)],normalize)
test_55x[,c(1,2,5)] <- lapply(test_55x[,c(1,2,5)],normalize)

train_65x[,c(1,2,5)] <- lapply(train_65x[,c(1,2,5)],normalize)
test_35x[,c(1,2,5)] <- lapply(test_35x[,c(1,2,5)],normalize)

train_85x[,c(1,2,5)] <- lapply(train_85x[,c(1,2,5)],normalize)
test_15x[,c(1,2,5)] <- lapply(test_15x[,c(1,2,5)],normalize)

```

# For training subsets,convert categorical variables into numerical types
```{r, warning=FALSE}
train_45x$FLAG_OWN_REALTY <- ifelse(train_45x$FLAG_OWN_REALTY=="Y",1,0)
train_65x$FLAG_OWN_REALTY <- ifelse(train_65x$FLAG_OWN_REALTY=="Y",1,0)
train_85x$FLAG_OWN_REALTY <- ifelse(train_85x$FLAG_OWN_REALTY=="Y",1,0)

education45 <-as.data.frame(dummy.code(train_45x$NAME_EDUCATION_TYPE))
education65 <-as.data.frame(dummy.code(train_65x$NAME_EDUCATION_TYPE))
education85 <-as.data.frame(dummy.code(train_85x$NAME_EDUCATION_TYPE))

child45 <- as.data.frame(dummy.code(train_45x$CNT_CHILDREN))
child65 <- as.data.frame(dummy.code(train_65x$CNT_CHILDREN))
child85 <- as.data.frame(dummy.code(train_85x$CNT_CHILDREN))

train_45x <- cbind(train_45x,education45,child45)
train_45x <- train_45x %>% select(-one_of(c("NAME_EDUCATION_TYPE", "CNT_CHILDREN")))

train_65x <- cbind(train_65x,education65,child65)
train_65x <- train_65x %>% select(-one_of(c("NAME_EDUCATION_TYPE", "CNT_CHILDREN")))

train_85x <- cbind(train_85x,education85,child85)
train_85x <- train_85x %>% select(-one_of(c("NAME_EDUCATION_TYPE", "CNT_CHILDREN")))
```

# For testing subsets,convert categorical variables into numerical types
```{r, warning=FALSE}
test_55x$FLAG_OWN_REALTY <- ifelse(test_55x$FLAG_OWN_REALTY=="Y",1,0)
test_35x$FLAG_OWN_REALTY <- ifelse(test_35x$FLAG_OWN_REALTY=="Y",1,0)
test_15x$FLAG_OWN_REALTY <- ifelse(test_15x$FLAG_OWN_REALTY=="Y",1,0)

education45t <-as.data.frame(dummy.code(test_55x$NAME_EDUCATION_TYPE))
education65t <-as.data.frame(dummy.code(test_35x$NAME_EDUCATION_TYPE))
education85t <-as.data.frame(dummy.code(test_15x$NAME_EDUCATION_TYPE))

child45t <- as.data.frame(dummy.code(test_55x$CNT_CHILDREN))
child65t <- as.data.frame(dummy.code(test_35x$CNT_CHILDREN))
child85t <- as.data.frame(dummy.code(test_15x$CNT_CHILDREN))

test_55x <- cbind(test_55x,education45t,child45t)
test_55x <- test_55x %>% select(-one_of(c("NAME_EDUCATION_TYPE", "CNT_CHILDREN")))

test_35x <- cbind(test_35x,education65t,child65t)
test_35x <- test_35x %>% select(-one_of(c("NAME_EDUCATION_TYPE", "CNT_CHILDREN")))

test_15x <- cbind(test_15x,education85t,child85t)
test_15x <- test_15x %>% select(-one_of(c("NAME_EDUCATION_TYPE", "CNT_CHILDREN")))
```

# Remove useless data
```{r, warning=FALSE}
rm(list = c("data1","data2","data3","train_45","train_65","train_85","test_55",
            "test_35","test_15","education45","education45t","education65","education65t",
            "education85","education85t","child45","child45t","child65","child65t",
            "child85","child85t"))
```


# KNN model
```{r, warning=FALSE}
# Optimizing
train_45y <- ifelse(train_45y==1,"1","0")
test_55y <- ifelse(test_55y==1,"1","0")
i=1
k.optm=1
for(i in 1:10){
  knn.model <- knn(train=train_45x,test=test_55x,cl=train_45y,k = i)
  k.optm[i] <- 100 * sum(test_55y == knn.model)/NROW(test_55y)
  k=i
  cat(k,'=',k.optm[i],'
')
}

# Accuracy plot
plot(k.optm, type="b", xlab="K- Value",ylab="Accuracy level")

model45 <- knn(train=train_45x,test=test_55x,cl=train_45y,k=7)
confusionMatrix(model45, as.factor(test_55y))
```

# Roc plot
```{r,warning=FALSE}
library(pROC)
pROC_obj <- roc(test_55y,as.numeric(model45),
            smoothed = TRUE,
            plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE,
            print.auc=TRUE, show.thres=TRUE)
```


```{r, warning=FALSE}
train_65y <- ifelse(train_65y==1,"1","0")
sqrt(nrow(train_65x))
model65 <- knn(train=train_65x,test=test_35x,cl=train_65y,k=7)

test_35y <- ifelse(test_35y==1,"1","0")
confusionMatrix(model65, as.factor(test_35y))
```

# Roc plot
```{r,warning=FALSE}
pROC_obj1 <- roc(test_35y,as.numeric(model65),
            smoothed = TRUE,
            plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE,
            print.auc=TRUE, show.thres=TRUE)
```


```{r, warning=FALSE}
train_85y <- ifelse(train_85y==1,"1","0")
sqrt(nrow(train_85x))
model85 <- knn(train=train_85x, test=test_15x,cl=train_85y,k=7)

test_15y <- ifelse(test_15y==1,"1","0")
confusionMatrix(model85, as.factor(test_15y))
```

# Roc plot
```{r,warning=FALSE}
pROC_obj2 <- roc(test_15y,as.numeric(model85),
            smoothed = TRUE,
            plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE,
            print.auc=TRUE, show.thres=TRUE)
```
